PANCHANGE_analysis

### 2020-08-19 PANCHANGE_analysis.Rmd
fixed the joining chunk

```{r}
diff_score_cols <- dat %>%
  select(contains("diff_score")) %>% 
  colnames()

diff_score_cols
```

@@

```{r vector with psychiatric disorders}
disorder_columns <- c(
    "depressive_disorders_numeric",
    "anxiety_disorders_numeric",
    "eating_disorders_numeric",
    "obsessive_compulsive_disorders_numeric",
    "psychotic_disorders_numeric",
    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
    "mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric",
    "mhd.attention_deficit_hyperactivity_disorder_numeric",
    "mhd.personality_disorder_numeric"
)
```

```{r gather to long format}
dat.long <- dat %>%
  gather(
    key = "Disorder",
    value = "Diagnosis",
    all_of(disorder_columns)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    all_of(diff_score_cols),
    Disorder,
    Diagnosis
  )

@@

## Disorders - Frequencies *use this as example to convert chunk above*
```{r Disorders - Frequencies}
#0 = No to disorder; 1 = Yes to disorder
dat.long %>%
  select(ID, #need to add columns for which you want summaries for 
         dem.sex,
         starts_with("mhd.") & ends_with("numeric")) %>%
  gather(
    key = "Disorder",
    value = "Diagnosis",
    mhd.MDD_numeric:mhd.ADHD_numeric #all the columns that we want to be gathered
  ) %>%
  group_by(Disorder) %>%
  count(Diagnosis) #count for diagnoses
```

@@

>>>>

```{r Vectors with diff_score_cols}
diff_score_cols <- dat %>%
  select(contains("diff_score")) %>% 
  colnames()

diff_score_cols

phq.diff_score_cols <- dat %>%
  select(contains("phq")) %>%
  select(contains("diff_score")) %>% 
  colnames()

phq.diff_score_cols

gad.diff_score_cols <- dat %>%
  select(contains("gad")) %>%
  select(contains("diff_score")) %>% 
  colnames()

gad.diff_score_cols

ocir.diff_score_cols <- dat %>%
  select(contains("ocir")) %>%
  select(contains("diff_score")) %>% 
  colnames()

ocir.diff_score_cols
```

@@

```{r vector with psychiatric disorders}
disorder_columns <- c(
    "depressive_disorders_numeric",
    "anxiety_disorders_numeric",
    "eating_disorders_numeric",
    "obsessive_compulsive_disorders_numeric",
    "psychotic_disorders_numeric",
    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
    "mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric",
    "mhd.attention_deficit_hyperactivity_disorder_numeric",
    "mhd.personality_disorder_numeric",
    "control_numeric"
)
```

```{r gather to long format Disorder}
dat.long <- dat %>%
  gather(
    key = "Disorder",
    value = "Diagnosis",
    all_of(disorder_columns)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    all_of(diff_score_cols),
    Disorder,
    Diagnosis
  )

@@

@@

Questionnaire columns
```{r Questionnaire columns}

```{r gather to long format Time_points}
dat.long.gad.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "gad.diff_score",
    all_of(gad.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Time_point_raw,
    gad.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "gad.diff_score_", "")) %>%
  select(-Time_point_raw)

head(dat.long.gad.diff)
```

```{r}
dat.long.gad.diff %>%
  ggplot(mapping = aes(y = gad.diff_score)) +
  geom_bar() +
  theme_minimal() +
  facet_wrap(facets = vars(Time_point))
```

```{r gather to long format Time_points}
dat.long.phq.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "phq.diff_score",
    all_of(phq.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Time_point_raw,
    phq.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "phq.diff_score_", "")) %>%
  select(-Time_point_raw)

head(dat.long.phq.diff)
```

```{r}
dat.long.phq.diff %>%
  ggplot(mapping = aes(y = phq.diff_score)) +
  geom_bar() +
  theme_minimal() +
  facet_wrap(facets = vars(Time_point))
```

```{r gather to long format Time_points}
dat.long.ocir.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "ocir.diff_score",
    all_of(ocir.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Time_point_raw,
    ocir.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "ocir.diff_score_", "")) %>%
  select(-Time_point_raw)

head(dat.long.ocir.diff)
```

```{r}
dat.long.ocir.diff %>%
  ggplot(mapping = aes(y = ocir.diff_score)) +
  geom_bar() +
  theme_minimal() +
  facet_wrap(facets = vars(Time_point))
```
